RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-26 manuscripts/manuscript.Rmd
included httr package name before citation

The `RNeXML` package is built for the NeXML Schema, [version 2009],
using the R software environment and the XML package for parsing and
generating XML `r citep(citation("XML"))`,  provides conversions into
the popular `phylo` format provided by the `ape` package `r citep(citation("ape"))`
`RNeXML` can automatically check taxonomic names and add taxonomic
identifiers when generating NeXML using methods from the `taxize` package `r citep(citation("taxize"))`.
Unique identifiers are provided with the `uuid` package `r citep(citation("uuid"))`,
and internet interfaces by the `r citep(citation("httr"))` package. The
packages `plyr` and `reshape2``r citep(c(citation("plyr"), citation("reshape2")))` are also imported for internal methods .

>>>>

The `RNeXML` package is built for the NeXML Schema, [version 2009],
using the R software environment and the XML package for parsing and
generating XML `r citep(citation("XML"))`,  provides conversions into
the popular `phylo` format provided by the `ape` package `r citep(citation("ape"))`
`RNeXML` can automatically check taxonomic names and add taxonomic
identifiers when generating NeXML using methods from the `taxize` package `r citep(citation("taxize"))`.
Unique identifiers are provided with the `uuid` package `r citep(citation("uuid"))`,
and internet interfaces by the `httr` package `r citep(citation("httr"))`. The
packages `plyr` and `reshape2``r citep(c(citation("plyr"), citation("reshape2")))` are also imported for internal methods .
